Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-10 VegOzone.tex
Fix typo of DO3SE

The results depicted in Fig.~\ref{fig:pody_rel} allow for a comprehensive assessment of a large variety of systematic uncertainties in the exposure-based risk metric for ozone induced damage in subarctic vegetation. In summary, we identify the following main effects of the bespoke parameterizations of the $DO_3SE$ model with respect to the MM default parameterization on ozone uptake:
\begin{itemize}
  \itemsep0pt
\item Increasing cold tolerance/heat intolerance $\Rightarrow$ increased uptake in both probed years,
\item usage of proper growing season $\Rightarrow$ reduced uptake with respect to the increase reported above,
\item an earlier assumed start of GS $\Rightarrow$ increased uptake,
\item drought conditions (SWP) $\Rightarrow$ reduced uptake,
\item lower/higher extent of stomatal opening at low light intensities $\Rightarrow$ increased/reduced uptake,
\item symmetric variation of the extent of stomatal opening at low light intensities $\Rightarrow$ asymmetric response in POD,
\item temperature acclimation $\Rightarrow$ amplifying effect on light threshold and drought effects.
\end{itemize}
The exact order of magnitude of these effects varies for individual species or PFTs and between years, but the predicted ozone uptake for the bespoke parameterization is always larger than for the MM default parameterizations and of the same order of magnitude as the variability between the years studied here. Although our temperature acclimations are hypothetical, they suggest considerable underestimations of ozone risk for subarctic species when compared to generic MM parameterizations. In particular, an earlier GS due to climate change, that is overlapping with the ozone spring peak, has the potential to increase the risk of ozone damage for vegetation with an acclimation to cold climates. Drought effects (SWP) do only matter if a bespoke GS is not taken into account. We will look at the specific species or PFTs in more detail in the following.

>>>>

The results depicted in Fig.~\ref{fig:pody_rel} allow for a comprehensive assessment of a large variety of systematic uncertainties in the exposure-based risk metric for ozone induced damage in subarctic vegetation. In summary, we identify the following main effects of the bespoke parameterizations of the $\mathrm{DO_3SE}$ model with respect to the MM default parameterization on ozone uptake:
\begin{itemize}
  \itemsep0pt
\item Increasing cold tolerance/heat intolerance $\Rightarrow$ increased uptake in both probed years,
\item usage of proper growing season $\Rightarrow$ reduced uptake with respect to the increase reported above,
\item an earlier assumed start of GS $\Rightarrow$ increased uptake,
\item drought conditions (SWP) $\Rightarrow$ reduced uptake,
\item lower/higher extent of stomatal opening at low light intensities $\Rightarrow$ increased/reduced uptake,
\item symmetric variation of the extent of stomatal opening at low light intensities $\Rightarrow$ asymmetric response in POD,
\item temperature acclimation $\Rightarrow$ amplifying effect on light threshold and drought effects.
\end{itemize}
The exact order of magnitude of these effects varies for individual species or PFTs and between years, but the predicted ozone uptake for the bespoke parameterization is always larger than for the MM default parameterizations and of the same order of magnitude as the variability between the years studied here. Although our temperature acclimations are hypothetical, they suggest considerable underestimations of ozone risk for subarctic species when compared to generic MM parameterizations. In particular, an earlier GS due to climate change, that is overlapping with the ozone spring peak, has the potential to increase the risk of ozone damage for vegetation with an acclimation to cold climates. Drought effects (SWP) do only matter if a bespoke GS is not taken into account. We will look at the specific species or PFTs in more detail in the following.
